Determining Maximum Allowable Current of an RBS using a Directed Graph Model and Greedy Algorithm

### 2024-02-11 paper/SST/3-main.tex
删除了main.tex中不必要的细节；删除了ref.bib中未引用文献
Add new files and update file modes

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage{setspace}
\usepackage[margin=1.25in]{geometry}
\usepackage{graphicx}
% \graphicspath{ {./figures/} }
\graphicspath{ {../figures/} }
% \graphicspath{ {../../attachments} }
\usepackage{subcaption} 
\usepackage{amsmath}
\usepackage{lineno}
\linenumbers

@@

%%%%%% Title %%%%%%
% Full titles can be a maximum of 100 characters, including spaces. 
% Title Format: Use title case, capitalizing the first letter of each word, except for certain small words, such as articles and short prepositions
% \title{Using a Directed Graph Model and Greedy Algorithm to Determine the Maximum Allowable Current in a Reconfigurable Battery System}
\title{Determining Maximum Allowable Current of an RBS using a Directed Graph Model and Greedy Algorithm}

@@

This paper has proposed a reliable and automated method to efficiently compute the MAC of an RBS.
The method is implemented using a greedy algorithm combined with an improved directed graph model.
Not only does the method provide the same global MAC calculation results as the brute-force method, but it also demonstrates superior computational efficiency to both the brute-force algorithm and the heuristic algorithms (SA and GA). 
Theoretically, for an RBS with $N_s$ switches and $N_b$ batteries, the efficiency of the proposed method is $N_s 2^{N_s - N_b} \log_{10} N_b$ times that of the brute-force method. 
This is primarily due to the utilization of the batteries' SPs guiding the RBS to reconfigure reasonable structures rather than blindly going through all possible structures.
Another advantage of this method is its capability to calculate the MACs of RBSs with arbitrary structures and varying batteries. 
Even in scenarios with random isolated batteries, the proposed method remains effective.
This method can facilitate the full utilization of the RBS's current output potential, guide the design and optimization of the RBS structure, and assist in evaluating the risk of current overload in practical applications.

@@

\begin{algorithm}
    \caption{Obtain the maximum available current (MAC) of a given RBS}\label{alg:greedy}
    \KwData{Directed graph model $G(V,E)$ of the RBS}
    \KwResult{$\max \eta$}
    \For{$i \in E_b$}{
        $P_i \leftarrow \{path| \text{starts at $v_1$ and ends at $v_n$} \}$\;
        $SP_i \leftarrow p_i \text{ which has the minimum}~\omega(p_i)~\text{among all}~p_i \in P_i. $
    }
    Get $\bm{A}$ by Eq. \ref{eq:A}\;
    \While{not yet determined $\max \eta$ }
    {
        $N_{\text{set}} \leftarrow$ number of selected SPs calculated by dichotomy\;
        $C_b    \leftarrow$ set of all combinations of $N_{\text{set}} $~batteries from $N_b$\;
        \For{$c_b \in C_b$}{
            $\bm{x}_s \leftarrow \text{list of all switches' states: $x_s[j]=1$ if $ j \in \bigcup_{i\in c_b}SP_i $ else 0}$\;
            $\bm{X} \leftarrow diag[1,1,\cdots,1,\bm{x}_s] $\;
            get $\bm{Y}_n$ by Eq. \ref{eq:Yn}\;
            \eIf{$\bm{Y}_n$ is invertible}{pass}{construct an effective solution}
            get $I_o$ by Eq. \ref{eq:I_o}\;
            get $\bm{I}_b$ by Eq. \ref{eq:I_b}\;
            \eIf{$\max(\bm{I}_b)\leq I_m$}{$\eta \leftarrow I_o/\max(\bm{I}_b)$\;}{break}
        }
    }
\end{algorithm}
% \begin{figure}[htbp]
%     \centering
%     \includegraphics[width=\textwidth]{algorithm.jpg}
% \end{figure}

@@

% \subsection*{Funding}
% 
% This work was supported by the National Natural Science Foundation of China (NSFC, No.52075028).

@@

% \begin{thebibliography}{10}
% 
% \bibitem{yangBatteryEnergyStorage2018}
% Yuqing Yang, Stephen Bremner, Chris Menictas, and Merlinde Kay.
% \newblock Battery energy storage system size determination in renewable energy systems: {{A}} review.
% \newblock {\em Renewable and Sustainable Energy Reviews}, 91:109--125, August 2018.
% 
% \bibitem{desiqueiraControlStrategySmooth2021}
% Luanna Maria~Silva {de Siqueira} and Wei Peng.
% \newblock Control strategy to smooth wind power output using battery energy storage system: {{A}} review.
% \newblock {\em Journal of Energy Storage}, 35:102252, March 2021.
% 
% \bibitem{schwanbeckInternationalSpaceStation2019}
% Eugene Schwanbeck and Penni Dalton.
% \newblock International {{Space Station Lithium-ion Batteries}} for {{Primary Electric Power System}}.
% \newblock In {\em 2019 {{European Space Power Conference}} ({{ESPC}})}, pages 1--1. {IEEE}, September 2019.
% 
% \bibitem{zhangDevelopmentProspectChinese2021}
% Lihua Zhang.
% \newblock Development and {{Prospect}} of {{Chinese Lunar Relay Communication Satellite}}.
% \newblock {\em Space: Science \& Technology}, 2021, January 2021.
% 
% \bibitem{choCommercialResearchBattery2015}
% Jaephil Cho, Sookyung Jeong, and Youngsik Kim.
% \newblock Commercial and research battery technologies for electrical energy storage applications.
% \newblock {\em Progress in Energy and Combustion Science}, 48:84--101, June 2015.
% 
% \bibitem{yangUnbalancedDischargingAging2016}
% Naixing Yang, Xiongwen Zhang, BinBin Shang, and Guojun Li.
% \newblock Unbalanced discharging and aging due to temperature differences among the cells in a lithium-ion battery pack with parallel combination.
% \newblock {\em Journal of Power Sources}, 306:733--741, February 2016.
% 
% \bibitem{fengPropagationMechanismsDiagnosis2019}
% Fei Feng, Xiaosong Hu, Lin Hu, Fengling Hu, Yang Li, and Lei Zhang.
% \newblock Propagation mechanisms and diagnosis of parameter inconsistency within {{Li-Ion}} battery packs.
% \newblock {\em Renewable and Sustainable Energy Reviews}, 112:102--113, September 2019.
% 
% \bibitem{jeevarajanBatterySafetyQualifications2012}
% J.~A. Jeevarajan and C.~Winchester.
% \newblock Battery {{Safety Qualifications}} for {{Human Ratings}}.
% \newblock {\em Interface magazine}, 21(2):51--55, January 2012.
% 
% \bibitem{pomboHybridPowerSystem2021}
% Daniel~V{\'a}zquez Pombo.
% \newblock A {{Hybrid Power System}} for a {{Permanent Colony}} on {{Mars}}.
% \newblock {\em Space: Science \& Technology}, 2021, January 2021.
% 
% \bibitem{hanNextGenerationBatteryManagement2020a}
% Weiji Han, Torsten Wik, Anton Kersten, Guangzhong Dong, and Changfu Zou.
% \newblock Next-{{Generation Battery Management Systems}}: {{Dynamic Reconfiguration}}.
% \newblock {\em IEEE Industrial Electronics Magazine}, 14(4):20--31, December 2020.
% 
% \bibitem{visairoReconfigurableBatteryPack2008}
% H.~Visairo and P.~Kumar.
% \newblock A reconfigurable battery pack for improving power conversion efficiency in portable devices.
% \newblock In {\em 2008 7th {{International Caribbean Conference}} on {{Devices}}, {{Circuits}} and {{Systems}}}, pages 1--6. {IEEE}, April 2008.
% 
% \bibitem{ci2007novel}
% Song Ci, Jiucai Zhang, Hamid Sharif, and Mahmoud Alahmad.
% \newblock A novel design of adaptive reconfigurable multicell battery for power-aware embedded networked sensing systems.
% \newblock In {\em IEEE GLOBECOM 2007-IEEE Global Telecommunications Conference}, pages 1043--1047. IEEE, 2007.
% 
% \bibitem{9209774}
% Jan Engelhardt, Tatiana Gabderakhmanova, Gunnar Rohde, and Mattia Marinelli.
% \newblock Reconfigurable stationary battery with adaptive cell switching for electric vehicle fast-charging.
% \newblock In {\em 2020 55th International Universities Power Engineering Conference (UPEC)}, pages 1--6, 2020.
% 
% \bibitem{engelhardt2021double}
% Jan Engelhardt, Jan~Martin Zepter, Tatiana Gabderakhmanova, Gunnar Rohde, and Mattia Marinelli.
% \newblock Double-string battery system with reconfigurable cell topology operated as a fast charging station for electric vehicles.
% \newblock {\em Energies}, 14(9):2414, 2021.
% 
% \bibitem{lawsonSoftwareConfigurableBattery2012}
% Barrie Lawson.
% \newblock A {{Software Configurable Battery}}.
% \newblock {\em EVS26 International Battery, Hybrid and Fuel Cell Electric Vehicle Symposium}, 2012.
% 
% \bibitem{he2014reconfiguration}
% Liang He, Linghe Kong, Siyu Lin, Shaodong Ying, Yu~Gu, Tian He, and Cong Liu.
% \newblock Reconfiguration-assisted charging in large-scale lithium-ion battery systems.
% \newblock In {\em 2014 ACM/IEEE International Conference on Cyber-Physical Systems (ICCPS)}, pages 60--71. IEEE, 2014.
% 
% \bibitem{kim2009dynamic}
% Hahnsang Kim and Kang~G Shin.
% \newblock On dynamic reconfiguration of a large-scale battery system.
% \newblock In {\em 2009 15th IEEE Real-Time and Embedded Technology and Applications Symposium}, pages 87--96. IEEE, 2009.
% 
% \bibitem{han2021analysis}
% Weiji Han, Anton Kersten, Changfu Zou, Torsten Wik, Xiaoliang Huang, and Guangzhong Dong.
% \newblock Analysis and estimation of the maximum switch current during battery system reconfiguration.
% \newblock {\em IEEE Transactions on Industrial Electronics}, 69(6):5931--5941, 2021.
% 
% \bibitem{chenSneakCircuitTheory2021}
% Si-Zhe Chen, Yule Wang, Guidong Zhang, Le~Chang, and Yun Zhang.
% \newblock Sneak {{Circuit Theory Based Approach}} to {{Avoiding Short-Circuit Paths}} in {{Reconfigurable Battery Systems}}.
% \newblock {\em IEEE Transactions on Industrial Electronics}, 68(12):12353--12363, 2021.
% 
% \bibitem{heExploringAdaptiveReconfiguration2013}
% Liang He, Lipeng Gu, Linghe Kong, Yu~Gu, Cong Liu, and Tian He.
% \newblock Exploring {{Adaptive Reconfiguration}} to {{Optimize Energy Efficiency}} in {{Large-Scale Battery Systems}}.
% \newblock In {\em 2013 {{IEEE}} 34th {{Real-Time Systems Symposium}}}, pages 118--127, December 2013.
% 
% \bibitem{hongwenheStateofChargeEstimationLithiumIon2011}
% Hongwen He, Rui Xiong, Xiaowei Zhang, Fengchun Sun, and JinXin Fan.
% \newblock State-of-{{Charge Estimation}} of the {{Lithium-Ion Battery Using}} an {{Adaptive Extended Kalman Filter Based}} on an {{Improved Thevenin Model}}.
% \newblock {\em IEEE Transactions on Vehicular Technology}, 60(4):1461--1469, May 2011.
% 
% \bibitem{mousavig.VariousBatteryModels2014}
% S.M. Mousavi~G. and M.~Nikdel.
% \newblock Various battery models for various simulation studies and applications.
% \newblock {\em Renewable and Sustainable Energy Reviews}, 32:477--485, April 2014.
% 
% \bibitem{ciNovelDesignAdaptive2007}
% Song Ci, Jiucai Zhang, Hamid Sharif, and Mahmoud Alahmad.
% \newblock A {{Novel Design}} of {{Adaptive Reconfigurable Multicell Battery}} for {{Power-Aware Embedded Networked Sensing Systems}}.
% \newblock In {\em {{IEEE GLOBECOM}} 2007-2007 {{IEEE Global Telecommunications Conference}}}, pages 1043--1047, November 2007.
% 
% \bibitem{alahmadBatterySwitchArray2008}
% Mahmoud Alahmad, Herb Hess, Mohammad Mojarradi, William West, and Jay Whitacre.
% \newblock Battery switch array system with application for {{JPL}}'s rechargeable micro-scale batteries.
% \newblock {\em Journal of Power Sources}, 177(2):566--578, March 2008.
% 
% \bibitem{kimDependableEfficientScalable2010b}
% Hahnsang Kim and Kang~G. Shin.
% \newblock Dependable, efficient, scalable architecture for management of large-scale batteries.
% \newblock In {\em Proceedings of the 1st {{ACM}}/{{IEEE International Conference}} on {{Cyber-Physical Systems}}}, {{ICCPS}} '10, pages 178--187, {New York, NY, USA}, April 2010. {Association for Computing Machinery}.
% 
% \bibitem{kimBalancedReconfigurationStorage2011a}
% Younghyun Kim, Sangyoung Park, Yanzhi Wang, Qing Xie, Naehyuck Chang, Massimo Poncino, and Massoud Pedram.
% \newblock Balanced reconfiguration of storage banks in a hybrid electrical energy storage system.
% \newblock In {\em 2011 {{IEEE}}/{{ACM International Conference}} on {{Computer-Aided Design}} ({{ICCAD}})}, pages 624--631, November 2011.
% 
% \bibitem{taesickimSeriesconnectedSelfreconfigurableMulticell2012a}
% Taesic Kim, Wei Qiao, and Liyan Qu.
% \newblock A series-connected self-reconfigurable multicell battery capable of safe and effective charging/discharging and balancing operations.
% \newblock In {\em 2012 {{Twenty-Seventh Annual IEEE Applied Power Electronics Conference}} and {{Exposition}} ({{APEC}})}, pages 2259--2264, February 2012.
% 
% \bibitem{6843711}
% Liang He, Linghe Kong, Siyu Lin, Shaodong Ying, Yu~Gu, Tian He, and Cong Liu.
% \newblock Reconfiguration-assisted charging in large-scale {{Lithium-ion}} battery systems.
% \newblock In {\em 2014 {{ACM}}/{{IEEE International Conference}} on {{Cyber-Physical Systems}} ({{ICCPS}})}, pages 60--71, April 2014.
% 
% \end{thebibliography}

% \printbibliography

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage{setspace}
\usepackage[margin=1.25in]{geometry}
\usepackage{graphicx}
% \graphicspath{ {./figures/} }
\graphicspath{ {../figures/} }
\usepackage{subcaption} 
\usepackage{amsmath}
\usepackage{lineno}
\linenumbers

@@

%%%%%% Title %%%%%%
% Full titles can be a maximum of 100 characters, including spaces. 
% Title Format: Use title case, capitalizing the first letter of each word, except for certain small words, such as articles and short prepositions
\title{Determining Maximum Allowable Current of an RBS using a Directed Graph Model and Greedy Algorithm}

@@

This paper has proposed a reliable and automated method to efficiently compute the MAC of an RBS.
The method is implemented using a greedy algorithm combined with an improved directed graph model.
Not only does the method provide the same global MAC calculation results as the brute-force method, but it also demonstrates superior computational efficiency to both the brute-force algorithm and the heuristic algorithms (SA and GA). 
Theoretically, for an RBS with $N_s$ switches and $N_b$ batteries, the efficiency of the proposed method is $N_s 2^{N_s - N_b} \log_{10} N_b$ times that of the brute-force method. 
This is primarily due to the utilization of the batteries' SPs guiding the RBS to reconfigure reasonable structures rather than blindly going through all possible structures.
Another advantage of this method is its capability to calculate the MACs of RBSs with arbitrary structures and varying batteries. 
Even in scenarios with random isolated batteries, the proposed method remains effective.
Accordingly, this proposed method can facilitate the full utilization of the RBS's current output potential, guide the design and optimization of the RBS structure, and assist in evaluating the risk of current overload in practical applications.
Its further application potentially focuses on the future explorations in battery energy management of the space power system in a spacecraft, to open new avenues for enhancing its efficiency and reliability.

@@

\begin{algorithm}
    \caption{Obtain the maximum available current (MAC) of a given RBS}\label{alg:greedy}
    \KwData{Directed graph model $G(V,E)$ of the RBS}
    \KwResult{$\max \eta$}
    \For{$i \in E_b$}{
        $P_i \leftarrow \{path| \text{starts at $v_1$ and ends at $v_n$} \}$\;
        $SP_i \leftarrow p_i \text{ which has the minimum}~\omega(p_i)~\text{among all}~p_i \in P_i. $
    }
    Get $\bm{A}$ by Eq. \ref{eq:A}\;
    \While{not yet determined $\max \eta$ }
    {
        $N_{\text{set}} \leftarrow$ number of selected SPs calculated by dichotomy\;
        $C_b    \leftarrow$ set of all combinations of $N_{\text{set}} $~batteries from $N_b$\;
        \For{$c_b \in C_b$}{
            $\bm{x}_s \leftarrow \text{list of all switches' states: $x_s[j]=1$ if $ j \in \bigcup_{i\in c_b}SP_i $ else 0}$\;
            $\bm{X} \leftarrow diag[1,1,\cdots,1,\bm{x}_s] $\;
            get $\bm{Y}_n$ by Eq. \ref{eq:Yn}\;
            \eIf{$\bm{Y}_n$ is invertible}{pass}{construct an effective solution}
            get $I_o$ by Eq. \ref{eq:I_o}\;
            get $\bm{I}_b$ by Eq. \ref{eq:I_b}\;
            \eIf{$\max(\bm{I}_b)\leq I_m$}{$\eta \leftarrow I_o/\max(\bm{I}_b)$\;}{break}
        }
    }
\end{algorithm}

@@

@@
